%last update Dec 28, 2002
\documentclass{amsart}
\usepackage{verbatim}
\pagestyle{plain}
\def\labelitemi{\bf --}
\begin{document}
\section*{Curriculum Michel Van den Bergh}
\section*{Personal data} \begin{itemize}
\item
Birthdate : 25-7-60\footnote{All dates are in the day-month-year
format}
\item
%Marriage : 9-1-88
%\item
Spouse : Gerda Bust
%\item
%Profession of spouse : Teacher computer science
\item
Children : Bertold (9-8-90) and Sarah (3-3-99).
%\item
%Born : 9-8-90
\end{itemize}
\section*{Employment}
\begin{itemize}
\item
1-9-82 to 31-7-87, Researcher at the FWO\footnote{The FWO is the Belgian
equivalent of for example the CNRS in France or the NSF in the USA}.
\item
1-9-85 to 31-12-85, Instructor at the Massachusetts.
Institute of Technology (MIT), Cambridge, Massachusetts.
\item
15-8-87 to 1-7-88, C.L.E.~Moore Instructor at the MIT.
\item
1-10-88 to 31-12-88, Assistant UIA\footnote{UIA is the main university in
Antwerp}.
\item
1-1-89 to 31-12-90, Senior researcher at the FWO.
\item
1-1-91 to 30-9-91, Assistant UIA.
\item
1-10-91 to 30-9-92, Visiting position at the Institut des Hautes Etudes
Scientifiques (IHES), Paris.
\item
1-10-92 to 1-10-95, Professor at the Institut Louis Pasteur,
Strasbourg (tenured position).
\item
1-10-93 to -, Director of research at the FWO
(``onderzoeksleider''). 
\item
1-10-94 to -, part time appointment at the ``Free University Of Brussels''.
\item
15-1-95 to 31-5-95, Visiting Associate Professor at MIT.
\item
1-1-98 to 23-7-98, Visiting Professor at MIT.
\item
1-2-00 to 30-4-00, Visiting ``Key Senior Scientist'' at the
Mathematical Sciences Research Institute (MSRI) te Berkeley (USA). 
\item 
22-12-03 to 18-6-04, Visiting position at tbe Mittag Leffler Institute in
Stockholm.
\item
15-06-06 to 15-07-06, Invited professor at Paris 7. 
\end{itemize}
\section*{Scientific carreer}
\begin{itemize}
\item
10-7-79 to 7-7-82, Under graduate degree at the UIA (greatest distinction)
\item
22-3-85, PhD in Mathematics, UIA
\item
17-5-90, ``Hoger Aggregaat\footnote{equivalent of ``Habilitation''}'', UIA
\end{itemize}
\section*{Scientific distinctions}
\begin{itemize}
\item
20-12-87, Laureat of the Belgian Academy of Sciences
\item 
7-6-97, Five-yearly ``Alumni Prize'' in mathematics.
\item
23-6-2003, ``Francqui Prize'' (interdisciplinary prize by the Belgian
Francqui Foundation).
\end{itemize}
\section*{Organization of conferences}
I was/am co-organizor of the following conferences.
\begin{itemize}
\item 14-2-2000 to 25-2-2000, MSRI, Interactions between algebraic geometry
  and non-commutative algebra.
\item 14-4-2002 to 20-04-2002, OberWolfach, Interactions between
  algebraic geometry and non-commutative algebra. 
\item 12-1-2004 to 16-1-2004, Mittag-Leffler Institute, Non-commutative
algebraic geometry.
\item 9-8-04 to 27-08-04, International Centre for Theoretical
  Physics, Advanced summer school and workshop on non-commutative
  algebraic geometry.
\item 22-10-2004 to 24-10-2004, Brussels, Francqui colloquium 
``Homological geometry''.
\item 7-5-2006 to 13-5-2006, OberWolfach, Interactions between
  algebraic geometry and non-commutative algebra.
\item 18-9-2006 to 22-9-2006, Shanghai, Workshop on non-commutative algebraic
geometry.
\end{itemize}
I was in the Scientific Advisory Panel for
\begin{itemize}
\item 18-12-2006 to 22-12-2006, Newton Institute Cambridge, Trends in Noncommutative Geometry.
\end{itemize}
\section*{Scientific responsabilities}
\begin{itemize}
\item Editor ``Advances in Mathematics''
\item Editor ``Journal of Algebra.''
\item Editor ``Bulletin of the Belgian Mathematical Society''
\item Editor ``Algebras and Representation Theory''
\item Editor ``Journal of Noncommutative Geometry''
\item Editor ``Journal of Algebra and Number Theorey''
\end{itemize}
\section*{Phd-students}
\noindent Previous:
\begin{itemize}
\item Bert Sevenhant (1-10-01): Wild quivers: on a conjecture of Kac
  and the Ringel-Hall algebra.
\item Martine Van Gastel (4-1-02): The local and global structure of
  non-commutative projective planes.
\item
Wendy Lowen (18-3-05): Deformation theory and Hochschild cohomology
of abelian categories.
\item Koen de Naeghel (27-2-06):  Ideals of three dimensional
Artin-Schelter regular algebras.
\end{itemize}
Current:
\begin{itemize}
\item Adam Van Roosmalen
\end{itemize}
\input{pub.tex}

\section*{Invited Lectures and stays abroad}
\begin{enumerate}
\item
29-1-84 to 4-2-84, Oberwolfach, lecture at the
conference ``Brauergroups of Fields''.
\item
26-8-84 to 1-8-84, Luminy, lecture at the
conference ``Ring Theory''.
\item
23-1-86, Paris, lecture at the Seminar Malliavin.
\item
27-6-87, Zurich, lecture at the Seminar P.~Gabriel.
\item
4-11-87, Yale Univ., Colloquim lecture.
\item
12-11-87, Brandeis Univ., lecture at the MIT, Harvard, Brandeis colloquim.
\item
29-5-88 to 4-6-88, OberWolfach, lecture at the conference
``Orders and their applications".
\item
26-12-88 to 1-1-89,
Jerusalem, lecture on the conference in honor of S.A.\ Amitsur sixtieth
birthday.
\item
8-1-89 to 11-1-89, Beer Sheeba, lecture at a conference on ``Hopf
algebras''. 
\item
20-3-89, Paris, lecture at the  seminar Malliavin.
\item
29-5-89, Paris, lecture at the  seminar Malliavin.
\item
4-6-89 to 10-6-89, Oberwolfach, lecture at the conference
``Rings and modules''.
\item
10-6-89 to 21-6-89, Berkeley, lecture at the conference ``Micro
program on non-commutative rings''.
\item
9-11-89, Utrecht, colloquim lecture at the State University of Utrecht.
\item
19-2-90, Paris, lecture at the seminar Malliavin.
\item
10-12-90, Paris, lecture at the seminar Malliavin.
\item
8-9-91, Paris, lecture at the enveloping algebra seminar.
\item
13-1-92, Paris, lecture at the seminar Alev, Levasseur, Peskine (formerly
organized by M.P.\ Malliavin).
\item
30-6-92 Paris, lecture at the conference on Invariant Theory.
\item
16-6-92, Orsay, lecture at the seminar on Algebraic geometry.
\item
14-1-92, Grenoble, seminar lecture.
\item
29-1-92, Strasbourg, seminar lecture.
\item
30-1-92, Strasbourg, seminar lecture.
\item
12-3-92, Reims, seminar lecture.
\item
1-2-93, Paris, lecture at the seminar ALP.
\item
15-4-94, Edinburgh, lecture at the Scottish Algebra day.
\item
2-9-94 to 11-9-94, Zurich, section talk at the International Congress
of Mathematicians (ICM94)
\item
25-7-94 to 29-7-94, Almeria, lecturer in a Spanish summerschool on
quantumspaces.
\item
14-11-94, Paris, lecture at the seminar ALP.
\item
18-11-94, Paris, lecture at the enveloping algebra seminar.
\item 
27-6-95 to 30-6-95, Reims, invited lecture at ``Conctact
Franco-Belge''.
\item
29-7-95 to 4-8-95, OberWolfach, lecture in the conference on
``Enveloping Algebras''.
\item
20-9-95, Paris, lecture at the seminar ALP.
\item 22-5-96 to 25-5-96, Antwerp, plenary lecture on the ``Joint
  meeting of the Americal Mathematical Society and the Benelux
  Mathematical Societies''.
\item
19-6-96 to 21-6-96, Paris, lecture on the ``Journees Solstice d'ete''.
\item
17-6-96 to 18-6-96, Louvain la Neuve, lecture at the
``Euroconference on Linear Algebraic Groups and Related Structures''
\item 
23-5-97, Lyon, lecture at the Journee d'Algebre.
\item
10-10-97, Copenhagen, seminar lecture.
\item
16-11-97 to 22-11-97, OberWolfach, lecture at ``Enveloping
Algebras and Representation Theory''. 
\item
17-8-97 to 23-8-97, Oberwolfach, lecture at ``Noncommutative
algebra and representation theory''.
\item 
1-6-98,2-6-98, Univ. of Washington, algebra seminar lectures.
\item
4-6-98, Eugene, Univ. of Oregon, colloquim lecture.
\item
5-6-98, Eugene, Univ. of Oregon, algebra seminar lecture.
\item
4-9-98, Bielefeld, plenary lecture on ICRTA8.5.
\item
3-4-98, MIT, lecture in the seminar on infinite dimensional Lie
algebras.
\item 11-5-98, Boston, North Eastern Univ., lecture in
representation theory seminar.
\item
Feb.\ '98-May '98, MIT, weekly series of lectures on
``non-commutative blowing up''.
\item
16-10-98, Paris, lecture in the seminar on enveloping
algebras.
\item
19-10-98, Paris, lecture in the seminar Alev, Keller, Levasseur,
Peskine.
\item 8-4-99, Bonn, lecture in the seminar on ``Non-commutative
  algebraic geometry'' at the ``Max Planck Institute fur
  Mathematik''. 
\item 29-5-99 to 1-6-99, St John's, Canada, plenary lecture at the
  summer meeting of the Canadian Mathematical Society.
\item 24-6-99 to 15-7-99, Bonn, lecture at a workshop on
  ``Non-commutative algebraic geometry'' at the MPI.
\item 16-12-99, Utrecht, Colloquim lecture. 
\item 1-2-00 to 31-5-00, 6 lectures in a seminar on non-commutative geometry.
\item 15-9-00 to 1-10-00, Bonn, lecture at a workshop on
  ``Non-commutative algebraic geometry'' at the MPI.
\item 21-5-01, Paris, Lecture in the seminar Alev, Keller, Levasseur,
Peskine.
\item  23-6-01 to 29-6-01, Beer-Sheva, Plenary speaker on the Amitsur
memorial symposium.
\item 25-1-02 to 31-1-02, Paris, Lecture in the seminar Alev, Keller, Levasseur,
Peskine and a
\item Lecture in  the seminar on enveloping algebras.
\item 28-04-02 to 04-05-02, OberWolfach, Lecture at the conference on
``Enveloping Algebras''.

\item 03-06-02 to 08-06-02, Oslo, Lecture at the Abel bicentennial 
conference.
\item 02-09-02 to 08-09-02, Almeria, Two lectures at a conference
on non-commutative algebraic geometry.
\item 18-11-02 to 22-11-02, Fraueninsel, Germany, Two lectures
at the symposium ``Twenty years of tilting theory''.
\item 9-11-02 to 13-11-02, Luminy, Lecture at a conference on
``Quiver varieties''.
\item 29-12-2002 to 2-02-2003, Michigan, Visit to Toby Stafford (2 lectures). 
\item 3-02-03 to 7-02-03, Berkeley, Lecture at a conference on
``Commutative algebra''.
\item Feb' 03, Paris, Lecture in the Seminar Alev, Levasseur, Keller, Peskine.
\item 11-03-03 to 15-03-03, Manchester, Lecture at a conference on
  ``Geometric Representation and Invariant Theory''.
\item 2-06-03 to 06-06-03, Edinburgh, Tutorial lectures on applications
of derived categories to non-commutative algebra.
\item 14-07-03 to 18-07-03, Lisboa, Plenary lecture at a conference
  on ``Algebras, Rings and Modules''.
\item 27-10-03 to 31-10-03, Luminy, Lectures on ``Sch\'emas de Hilbert,
  alg\'ebre noncommutative et correspondance de McKay''.
\item 12-1-04 to 17-1-04, Stockholm, Lecture at workshop.
\item 14-6-04 to 21-7-04, Warwick, Lecture at workshop on non-commutative
geometry.
\item 2-8-04 to 7-8-04, Edinburgh, Lecture at workshop on ``Quivers and strings''.
\item 9-8-04 to 27-8-04, Trieste, Course on homological algebra at the
``International Center for Theoretical Physics''.
\item 26-8-04, Trieste, talk at workshop at the ``International Center for Theoretical Physics''.
\item 3-9-04 to 5-9-04, Matsumoto, 3 lectures on conference on ring theory.
\item 4-10-04, Paris, Lecture on a day in honor of Marie-Paule Malliavin.
\item 6-2-05 to 12-02-05, Oberwolfach, 2 lectures in the meeting ``Representation Theory of Finite-Dimensional Algebras''.
\item 17-4-05 to 14-5-05, Michigan, visit to Toby Stafford (no lecture).
\item 14-5-05 to 21-5-05, Toronto, visit to Buchweitz (no lecture).
\item 30-06-05, Bonn, lecture at the Max Planck Institute for Mathematics.
\item 1-07-05, Bonn, lecture at Bonn University.
\item 16-09-05 to 21-09-05, Spa, lecture in the ESF meeting ``Geometric 
Representation and Invariant Theory Algebraic Quantization and Deformations''.
\item 17-10-05 to 21-10-05, Mainz, 5 lectures on the ``Autumn school on
deformation theory''.
\item 1-04-06 to 6-04-06, Banff, Canada, Lecture at the conference
on ``Recent trends in higher dimensional geometry''. 
\item 7-05-06 to 13-05-06, Tokyo, Lecture at the conference ``Poisson 2006''.
\item 15-06-06 to 15-07-06, Paris, 3 lectures.
\item 16-09-06 to 28-09-06, Shanghai, lecture at Tiaotong University. 
\item 1-10-06 to 31-10-06, Cambridge, no lectures.
\item 10-10-06, Oxford, Lecture in the algebraic geometry seminar.  
\item 10-11-06, Strasbourg, Lecture in a conference on operads.
\item 11-11-06, Paderborn, Lecture at a conference in honor of Helmut Lenzing.
\item 1-4-2007 to 7-4-2007, Lyon, France, Lecture.
\item 26-8-2007 to 31-8-2007, Konstanz, Germany, 3 lectures on a summerschool devoted to
  de Jong's theorem.
\item 10-9-2007 to 14-9-2007, Beijing, China, 3 lectures at the summerschool
  ``Workshop on Categorification, Quantization and Clusters'' at the
  Morning Side Center of Mathematics.
\item 18-9-2007 to 22-9-2007, Almeria, Spain, conference in honor of Fred Van
Oystaeyen. 
\item 1-11-07 to 30-11-07, Barcelona, Spain.
\item 5-5-2008 to 30-06-2008, Barcelona, Spain, plenary lecture at 
``HOCAT 2008 - Homotopy structures in geometry and algebra; derived categories,
higher categories''.
\end{enumerate}






\end{document}
~

