\documentclass{amsart}
\usepackage{verbatim}
\pagestyle{plain}
\def\labelitemi{\bf --}
\begin{document}
\section*{Curriculum Michel Van den Bergh}
\section*{Personal data} \begin{itemize}
\item
Birthdate : 25-7-60\footnote{All dates are in the day-month-year
format}
\item
%Marriage : 9-1-88
%\item
Spouse : Gerda Bust
%\item
%Profession of spouse : Teacher computer science
\item
Children : Bertold (9-8-90) and Sarah (3-3-99).
%\item
%Born : 9-8-90
\end{itemize}
\section*{Employment}
\begin{itemize}
\item
1-9-82 to 31-7-87, Researcher at the FWO\footnote{The FWO is the Belgian
equivalent of for example the CNRS in France or the NSF in the USA}.
\item
1-9-85 to 31-12-85, Instructor at the Massachusetts
Institute of Technology.
\item
15-8-87 to 1-7-88, C.L.E.~Moore Instructor at MIT.
\item
1-10-88 to 31-12-88, Assistant UIA\footnote{UIA is the main university in
Antwerp}.
\item
1-1-89 to 31-12-90, Senior researcher at the FWO.
\item
1-1-91 to 30-9-91, Assistant UIA.
\item
1-10-91 to 30-9-92, Visiting position at the Institut des Hautes Etudes
Scientifiques (IHES), Paris.
\item
1-10-92 to 1-10-95, Professor at the Institut Louis Pasteur,
Strasbourg (tenured position). Last two years on leave.
\item
1-10-93 to -, Director of research at the FWO
(``onderzoeksleider''). Home institution: Limburgs Universitair Centrum.
\item
1-10-94 to -, part time appointment at the ``Free University Of Brussels''.
\item
15-1-95 to 31-5-95, Visiting Associate Professor at MIT.
\item
1-1-98 to 23-7-98, Visiting Professor at MIT.
\item
1-2-00 to 30-4-00, Visiting ``Key Senior Scientist'' at the
Mathematical Sciences Research Institute (MSRI) te Berkeley (USA). 
\item 
22-12-03 to 18-6-04, Visiting position at tbe Mittag Leffler Institute in
Stockholm.
\end{itemize}
\section*{Scientific carreer}
\begin{itemize}
\item
10-7-79 to 7-7-82, Under graduate degree at the UIA (greatest distinction)
\item
22-3-85, PhD in Mathematics, UIA
\item
17-5-90, ``Hoger Aggregaat\footnote{equivalent of ``Habilitation''}'', UIA
\end{itemize}
\section*{Scientific distinctions}
\begin{itemize}
\item
20-12-87, Laureat of the Belgian Academy of Sciences
\item 
7-6-97, Five-yearly ``Alumni Prize'' in mathematics.
\item
23-6-2003, ``Francqui Prize'' (interdisciplinary prize by the Belgian
Francqui Foundation).
\end{itemize}
\section*{Organization of conferences}
I am(was) (co)organizor of the following conferences.
\begin{itemize}
\item 14-2-2000 to 25-2-2000, MSRI, Interactions between algebraic geometry
  and non-commutative algebra.
\item 14-4-2002 to 20-04-2002, OberWolfach, Interactions between
  algebraic geometry and non-commutative algebra. 
\item 12-1-2004 to 16-1-2004, Mittag-Leffler Institute, Non-commutative
algebraic geometry.
\item 9-8-04 to 27-08-04, International Centre for Theoretical
  Physics, Advanced summer school and workshop on non-commutative
  algebraic geometry.
\item 22-10-2004 to 24-10-2004, Brussels, Francqui colloquium 
``Homological geometry''.
\item 7-5-2006 to 13-5-2006, OberWolfach, Interactions between
  algebraic geometry and non-commutative algebra.
\end{itemize}
\section*{Scientific responsabilities}
\begin{itemize}
\item Editor ``Advances in Mathematics''
\item Editor ``Journal of Algebra.''
\item Editor ``Bulletin of the Belgian Mathematical Society''
\item Editor ``Algebras and Representation Theory''
\end{itemize}
\section*{Phd-students}
\noindent Previous:
\begin{itemize}
\item Bert Sevenhant (1-10-01): Wild quivers: on a conjecture of Kac
  and the Ringel-Hall algebra.
\item Martine Van Gastel (4-1-02): The local and global structure of
  non-commutative projective planes.
\item
Wendy Lowen (18-3-05): Deformation theory and Hochschild cohomology
of abelian categories.
\end{itemize}
Current:
\begin{itemize}
\item Koen de Naeghel
\item Adam Van Roosmalen
\end{itemize}





\end{document}
~

