
\section*{Publications}
\subsection*{Monographs}

\begin{enumerate}

\item
L.~Le Bruyn, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Graded orders}, Birkhauser Boston Inc., Boston, MA, pp.~vi+208, 1988.

\item
I.~Reiten and M.~Van den Bergh, {\em Two-dimensional tame and maximal orders of finite representation type}, Mem. Amer. Math. Soc. {\bf 80} (1989), viii+72.

\item
I.~M.~Musson and M.~Van den Bergh, {\em Invariants under tori of rings of differential operators and related topics}, Mem. Amer. Math. Soc. {\bf 136} (1998), viii+85.

\item
M.~Van den Bergh, {\em Blowing up of non-commutative smooth surfaces}, Mem. Amer. Math. Soc. {\bf 154} (2001), x+140.

\end{enumerate}


\subsection*{Articles}

\begin{enumerate}
\setcounter{enumi}{4}
\item
M.~Van den Bergh, {\em A duality theorem for Hopf algebras}, Methods in ring theory (Antwerp, 1983), NATO Adv. Sci. Inst. Ser. C Math. Phys. Sci., vol.~129, Reidel, Dordrecht, pp.~517--522, 1984.

\item
S.~Caenepeel, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Generalized crossed products applied to maximal orders, Brauer groups and related exact sequences}, J. Pure Appl. Algebra {\bf 33} (1984), 123--149.

\item
M.~Van den Bergh and J.~Van Geel, {\em A duality theorem for orders in central simple algebras over function fields}, J. Pure Appl. Algebra {\bf 31} (1984), 227--239.

\item
M.~Van den Bergh and J.~Van Geel, {\em Algebraic elements in division algebras over function fields of curves}, Israel J. Math. {\bf 52} (1985), 33--45.

\item
M.~Van den Bergh, {\em On a theorem of Cohen and Montgomery}, Proc. Amer. Math. Soc. {\bf 94} (1985), 562--564.

\item
M.~Van den Bergh, {\em Graded Dedekind rings}, J. Pure Appl. Algebra {\bf 35} (1985), 105--115.

\item
M.~Van den Bergh, {\em A note on graded $K$-theory}, Comm. Algebra {\bf 14} (1986), 1561--1564.

\item
L.~Le Bruyn and M.~Van den Bergh, {\em An explicit description of $T_{3,2}$}, Ring theory (Antwerp, 1985), Lecture Notes in Math., vol.~1197, Springer, Berlin, pp.~109--113, 1986.

\item
L.~Le Bruyn, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Proj of generic matrices and trace rings}, Comm. Algebra {\bf 14} (1986), 1687--1706.

\item
M.~Van den Bergh, {\em The algebraic index of a division algebra}, Ring theory (Antwerp, 1985), Lecture Notes in Math., vol.~1197, Springer, Berlin, pp.~190--206, 1986.

\item
M.~Van den Bergh, {\em Regular rings of dimension three}, S\'eminaire d'alg\`ebre Paul Dubreil et Marie-Paule Malliavin (Paris, 1986), Lecture Notes in Math., vol.~1296, Springer, Berlin, pp.~228--234, 1987.

\item
M.~Van den Bergh, {\em A note on graded Brauer groups}, Bull. Soc. Math. Belg. S\'er. B {\bf 39} (1987), 177--179.

\item
M.~Van den Bergh, {\em Linearisations of binary and ternary forms}, J. Algebra {\bf 109} (1987), 172--183.

\item
L.~Le Bruyn and M.~Van den Bergh, {\em The ramification divisor of regular tame orders. I}, Comm. Algebra {\bf 15} (1987), 1815--1840.

\item
M.~Van den Bergh, {\em Division algebras over function fields of varieties}, Academiae Analecta {\bf 49} (1987), 127--135.

\item
M.~Van den Bergh, {\em The Brauer-Severi scheme of the trace ring of generic matrices}, Perspectives in ring theory (Antwerp, 1987), NATO Adv. Sci. Inst. Ser. C Math. Phys. Sci., vol.~233, Kluwer Acad. Publ., Dordrecht, pp.~333--338, 1988.

\item
L.~Le Bruyn and M.~Van den Bergh, {\em Regularity of trace rings of generic matrices}, J. Algebra {\bf 117} (1988), 19--29.

\item
M.~Awami, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Note on derivations of graded rings and classification of differential polynomial rings}, Bull. Soc. Math. Belg. S\'er. A {\bf 40} (1988), 175--183.

\item
M.~Van den Bergh, {\em Group rings over Dedekind rings}, Israel J. Math. {\bf 61} (1988), 295--300.

\item
M.~Van den Bergh, {\em Algebraic splitting fields of division algebras}, Ring theory 1989 (Ramat Gan and Jerusalem, 1988/1989), Israel Math. Conf. Proc., vol.~1, Weizmann, Jerusalem, pp.~381--388, 1989.

\item
M.~Van den Bergh, {\em The center of the generic division algebra}, J. Algebra {\bf 127} (1989), 106--126.

\item
C.~N{\u{a}}st{\u{a}}sescu, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Separable functors applied to graded rings}, J. Algebra {\bf 123} (1989), 397--413.

\item
M.~Van den Bergh, {\em Trace rings of generic matrices are Cohen-Macaulay}, J. Amer. Math. Soc. {\bf 2} (1989), 775--799.

\item
M.~J.~Asensio, M.~Van den Bergh, and F.~Van Oystaeyen, {\em A new algebraic approach to microlocalization of filtered rings}, Trans. Amer. Math. Soc. {\bf 316} (1989), 537--553.

\item
M.~Van den Bergh and F.~Van Oystaeyen, {\em Lifting maximal orders}, Comm. Algebra {\bf 17} (1989), 341--349.

\item
M.~Artin, J.~Tate, and M.~Van den Bergh, {\em Some algebras associated to automorphisms of elliptic curves}, The Grothendieck Festschrift, Vol.\ I, Progr. Math., vol.~86, Birkh\"auser Boston, Boston, MA, pp.~33--85, 1990.

\item
M.~Artin and M.~Van den Bergh, {\em Twisted homogeneous coordinate rings}, J. Algebra {\bf 133} (1990), 249--271.

\item
H.~S.~Li, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Note on the $K\sb 0$ of rings with Zariskian filtration}, $K$-Theory {\bf 3} (1990), 603--606.

\item
H.~S.~Li, M.~Van den Bergh, and F.~Van Oystaeyen, {\em Global dimension and regularity of Rees rings for non-Zariskian filtrations}, Comm. Algebra {\bf 18} (1990), 3195--3208.

\item
M.~Van den Bergh, {\em Differential operators on semi-invariants for tori and weighted projective spaces}, Topics in invariant theory (Paris, 1989/1990), Lecture Notes in Math., vol.~1478, Springer, Berlin, pp.~255--272, 1991.

\item
M.~Artin, J.~Tate, and M.~Van den Bergh, {\em Modules over regular algebras of dimension $3$}, Invent. Math. {\bf 106} (1991), 335--388.

\item
M.~Van den Bergh, {\em Cohen-Macaulayness of modules of covariants}, Invent. Math. {\bf 106} (1991), 389--409.

\item
L.~Le Bruyn and M.~Van den Bergh, {\em Algebraic properties of linear cellular automata}, Linear Algebra Appl. {\bf 157} (1991), 217--234.

\item
M.~Van den Bergh, {\em Cohen-Macaulayness of modules of invariants for $\rm {S}{L}\sb 2$}, J. Algebra {\bf 142} (1991), 273--284.

\item
M.~Van den Bergh, {\em Explicit rational forms for the Poincar\'e series of the trace rings of generic matrices}, Israel J. Math. {\bf 73} (1991), 17--31.

\item
C.~Apostolopoulos, M.~Van den Bergh, and F.~Van Oystaeyen, {\em On Schur rings of group rings of finite groups}, Comm. Algebra {\bf 20} (1992), 2139--2152.

\item
A.~Schofield and M.~Van den Bergh, {\em The index of a Brauer class on a Brauer-Severi variety}, Trans. Amer. Math. Soc. {\bf 333} (1992), 729--739.

\item
A.~Jensen, S.~J{\o}ndrup, and M.~Van den Bergh, {\em Artinian quotient rings of filtered rings}, J. Algebra {\bf 161} (1993), 230--236.

\item
L.~Le Bruyn and M.~Van den Bergh, {\em On quantum spaces of Lie algebras}, Proc. Amer. Math. Soc. {\bf 119} (1993), 407--414.

\item
M.~Van den Bergh, {\em Cohen-Macaulayness of semi-invariants for tori}, Trans. Amer. Math. Soc. {\bf 336} (1993), 557--580.

\item
M.~Van den Bergh, {\em Noncommutative homology of some three-dimensional quantum spaces}, Proceedings of Conference on Algebraic Geometry and Ring Theory in honor of Michael Artin, Part III (Antwerp, 1992), vol.~8, pp.~213--230, 1994.

\item
M.~Van den Bergh, {\em A converse to Stanley's conjecture for $\rm {S}l\sb 2$}, Proc. Amer. Math. Soc. {\bf 121} (1994), 47--51.

\item
A.~Schofield and M.~Van den Bergh, {\em Division algebra coproducts of index $n$}, Trans. Amer. Math. Soc. {\bf 341} (1994), 505--517.

\item
M.~Van den Bergh, {\em Modules of covariants}, Proceedings of the International Congress of Mathematicians, Vol.\ 1, 2 (Z\"urich, 1994), Birkh\"auser, Basel, pp.~352--362, 1995.

\item
J.~Tate and M.~Van den Bergh, {\em Homological properties of Sklyanin algebras}, Invent. Math. {\bf 124} (1996), 619--647.

\item
L.~Le Bruyn, S.~P.~Smith, and M.~Van den Bergh, {\em Central extensions of three-dimensional Artin-Schelter regular algebras}, Math. Z. {\bf 222} (1996), 171--212.

\item
M.~Van den Bergh, {\em A translation principle for the four-dimensional Sklyanin algebras}, J. Algebra {\bf 184} (1996), 435--490.

\item
M.~Van den Bergh, {\em Some rings of differential operators for $\rm {S}l\sb 2$-invariants are simple}, J. Pure Appl. Algebra {\bf 107} (1996), 309--335.

\item
J.~Alev, A.~Ooms, and M.~Van den Bergh, {\em A class of counterexamples to the Gelfand-Kirillov conjecture}, Trans. Amer. Math. Soc. {\bf 348} (1996), 1709--1716.

\item
M.~Van den Bergh, {\em Division algebras on ${\bf P}\sp 2$ of odd index, ramified along a smooth elliptic curve are cyclic}, Alg\`ebre non commutative, groupes quantiques et invariants (Reims, 1995), S\'emin. Congr., vol.~2, Soc. Math. France, Paris, pp.~43--53, 1997.

\item
M.~Van den Bergh and M.~Van Gastel, {\em Graded modules of Gelfand-Kirillov dimension one over three-dimensional Artin-Schelter regular algebras}, J. Algebra {\bf 196} (1997), 251--282.

\item
M.~Van den Bergh, {\em Existence theorems for dualizing complexes over non-commutative graded and filtered rings}, J. Algebra {\bf 195} (1997), 662--679.

\item
K.~E.~Smith and M.~Van den Bergh, {\em Simplicity of rings of differential operators in prime characteristic}, Proc. London Math. Soc. (3) {\bf 75} (1997), 32--62.

\item
M.~Van den Bergh, {\em A relation between Hochschild homology and cohomology for Gorenstein rings}, Proc. Amer. Math. Soc. {\bf 126} (1998), 1345--1348.

\item
T.~Gateva-Ivanova and M.~Van den Bergh, {\em Semigroups of $I$-type}, J. Algebra {\bf 206} (1998), 97--112.

\item
K.~Bauwens and M.~Van den Bergh, {\em Normalizing extensions of the two-Veronese of a three-dimensional Artin-Schelter regular algebra on two generators}, J. Algebra {\bf 205} (1998), 368--390.

\item
B.~Sevenhant and M.~Van den Bergh, {\em On the number of absolutely indecomposable representations of a quiver}, J. Algebra {\bf 221} (1999), 29--49.

\item
B.~Sevenhant and M.~Van den Bergh, {\em On the double of the Hall algebra of a quiver}, J. Algebra {\bf 221} (1999), 135--160.

\item
M.~Van den Bergh, {\em Local cohomology of modules of covariants}, Adv. Math. {\bf 144} (1999), 161--220.

\item
K.~Ajitabh and M.~Van den Bergh, {\em Presentation of critical modules of GK-dimension $2$ over elliptic algebras}, Proc. Amer. Math. Soc. {\bf 127} (1999), 1633--1639.

\item
J.~Alev, A.~I.~Ooms, and M.~Van den Bergh, {\em The Gelfand-Kirillov conjecture for Lie algebras of dimension at most eight}, J. Algebra {\bf 227} (2000), 549--581.

\item
M.~Van den Bergh, {\em Abstract blowing down}, Proc. Amer. Math. Soc. {\bf 128} (2000), 375--381.

\item
A.~Schofield and M.~Van den Bergh, {\em Semi-invariants of quivers for arbitrary dimension vectors}, Indag. Math. (N.S.) {\bf 12} (2001), 125--138.

\item
B.~Sevenhant and M.~Van den Bergh, {\em A relation between a conjecture of Kac and the structure of the Hall algebra}, J. Pure Appl. Algebra {\bf 160} (2001), 319--332.

\item
I.~Reiten and M.~Van den Bergh, {\em Grothendieck groups and tilting objects}, Algebr. Represent. Theory {\bf 4} (2001), 1--23.

\item
J.~T.~Stafford and M.~Van den Bergh, {\em Noncommutative curves and noncommutative surfaces}, Bull. Amer. Math. Soc. (N.S.) {\bf 38} (2001), 171--216 (electronic).

\item
I.~Reiten and M.~Van den Bergh, {\em Noetherian hereditary abelian categories satisfying Serre duality}, J. Amer. Math. Soc. {\bf 15} (2002), 295--366 (electronic).

\item
Y.~Berest and G.~Wilson, {\em Ideal classes of the Weyl algebra and noncommutative projective geometry (with an appendix by Michel Van den Bergh)}, Int. Math. Res. Not. {\bf 26} (2002), 1347--1396.

\item
M.~Van den Bergh, {\em Erratum to: ``A relation between Hochschild homology and cohomology for Gorenstein rings'' [Proc. Amer. Math. Soc. \bf 126 (1998), no. 5, 1345--1348; MR 99m:16013]}, Proc. Amer. Math. Soc. {\bf 130} (2002), 2809--2810 (electronic).

\item
M.~Van den Bergh and M.~Van Gastel, {\em On the structure of non-commutative regular local rings of dimension two}, Comm. Algebra {\bf 30} (2002), 4575--4588.

\item
M.~Van den Bergh, {\em Non-commutative crepant resolutions}, The Legacy of Niels Hendrik Abel, Springer, pp.~749--770, 2002.

\item
A.~Bondal and M.~Van den Bergh, {\em Generators and representability of functors in commutative and noncommutative geometry}, Moscow Mathematical Journal {\bf 3} (2003), 1--36.

\item
W.~Crawley-Boevey and M.~Van den Bergh, {\em Absolutely indecomposable representations and Kac-Moody Lie algebras}, Invent. Math. {\bf 155} (2004), 537--559.

\item
M.~Van den Bergh, {\em Three-dimensional flops and noncommutative rings}, Duke Math. J. {\bf 122} (2004), 423--455.

\item
K.~de Naeghel and M.~van den Bergh, {\em Ideal classes of three-dimensional Sklyanin algebras}, J. Algebra {\bf 276} (2004), 515--551.

\item
M.~Van den Bergh, {\em A remark on a theorem by Deligne}, Proc. Amer. Math. Soc. {\bf 132} (2004), 2857--2858 (electronic).

\item
K.~De Naeghel and M.~Van den Bergh, {\em Ideal classes of three dimensional Artin-Schelter regular algebras}, J. Algebra {\bf 283} (2005), 399--429.

\item
M.~Van den Bergh, {\em On the ${\mathbb Z}D\sb \infty$ category}, Proceedings of the 37th Symposium on Ring Theory and Representation Theory, Symp. Ring Theory Represent Theory Organ. Comm., Osaka, pp.~103--112, 2005.

\item
W.~Lowen and M.~Van den Bergh, {\em Hochschild cohomology of abelian categories and ringed spaces}, Adv. Math. {\bf 198} (2005), 172--221.

\item
W.~Lowen and M.~Van den Bergh, {\em Deformation theory of abelian categories}, Trans. Amer. Math. Soc. {\bf 358} (2006), 5441--5483.

\item
L.~Hille and M.~Van den Bergh, {\em Fourier-Mukai transforms}, Handbook of tiltingtheory, London Mathematical Society Lecture Note Series, vol.~332, Cambridge University Press, pp.~147--173, 2007.

\item
K.~De Naeghel and M.~Van den Bergh, {\em On incidence between strata of the Hilbert scheme of points on $\mathbb P\sp 2$}, Math. Z. {\bf 255} (2007), 897--922.

\item
M.~Van den Bergh, {\em On global deformation quantization in the algebraic case}, Journal of Algebra {\bf 315} (2007), 326--395.

\end{enumerate}


\subsection*{Accepted for publication}

\begin{enumerate}
\setcounter{enumi}{87}
\item
M.~Van den Bergh, {\em Double Poisson algebras}, to appear in Trans. Amer. Math. Soc.

\item
J.~T.~Stafford and M.~Van den Bergh, {\em Non-commutative resolutions and rational singularities}, to appear in the Michigan Journal of Mathematics.

\end{enumerate}


\subsection*{Submitted}

\begin{enumerate}
\setcounter{enumi}{89}
\item
D.~Calaque and M.~Van den Bergh, {\em Hochschild cohomology and Atiyah classes}, submitted.

\end{enumerate}


\subsection*{In preparation}

\begin{enumerate}
\setcounter{enumi}{90}
\item
S.~P.~Smith and M.~Van den Bergh, {\em Global dimension of primitive quotients of the four-dimensional Sklyanin algebra}, in preparation.

\item
M.~Van den Bergh, {\em Non-commutative quadrics}, in preparation.

\item
M.~Van den Bergh, {\em Non-commutative Hirzebruch surfaces}, in preparation.

\item
M.~Van den Bergh, {\em The non-commutative Cremona transform}, in preparation.

\item
D.~Calaque and M.~Van den Bergh, {\em Global formality in the $G_\infty$ case and compatibility with cup-product}, in preparation.

\end{enumerate}


\subsection*{Notes}

\begin{enumerate}
\setcounter{enumi}{95}
\item
M.~Van den Bergh, {\em Some generalities on $G$-equivariant quasi-coherent $O_X$ and $D_X$-modules}, notes.

\item
M.~Van den Bergh, {\em Notes on de Jong's period$=$index theorem for central simple algebras over fields of transcendence degree two}, notes.

\end{enumerate}

